The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
Old title restored

% first the title is needed
\title{Investment Strategy Based on Artificial Earthworm Behavior for Algotrading Application}

% a short form should be given in case it is too long for the running head
\titlerunning{Investment Strategy Based on Artificial Earthworm Behavior}

>>>>

% first the title is needed
\title{The investment strategy based on behavior of artificial earthworm for use in algotrading}

% a short form should be given in case it is too long for the running head
\titlerunning{The investment strategy based on behavior of artificial earthworm}
